Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-18 paper/paper.tex
polishing summary plot
added data to tables
pass on paper

\Mar{REVISE}The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the stability of the engines we analyzed
using the Test262 standard conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we conjecture that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs.

\subsection{Summary of Results}
\label{sec:summary}

Figure~\ref{fig:summary}...

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of results.}
\end{figure}

\subsection{Test Transplantation}
\label{sec:transplantation}
\label{sec:stability}

\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 2278 & - & - & - & - & - & - \\
    \veight{} & 1213 & - & - & - & - & - & - \\
    \chakra{} & 7041 & - & - & - & - & - & - \\
    \smonkey{} & 1761 & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

%% This suggests that the investiment in
%% testing paid off in this case.

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the stability of the engines we analyzed
using the official Test262 conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that the domain
of possible inputs is too large; consequently, we expect that test
suites written for a given engine cover scenarios and corner cases
uncovered by another engine. To sum, we conjecture that test cases
written for one engine could reveal bugs in different engines as
opposed to only manifesting false alarms. Third, we analyzed the
impact of using cross-engine differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
is that black-box fuzzers could expose important bugs.

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
summary of the bugs we reported. The figure shows the distribution of
status of bug reports per engine. Note that several of these reports
were not reviewed yet, \ie, they did not receive a label ``confirmed''
or ``rejected'' from the development team. Note also that we did not
find bugs in the Mozilla \smonkey\ engine and that several of the bugs
we reported were already fixed and incorporated to the latest release
of corresponding engines.

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 120 0 150,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of bug reports per engine and status.}
\end{figure}

\subsection{Conformance}
\label{sec:stability}

\begin{wraptable}[12]{r}{0.25\textwidth}  
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.\Mar{Please, use percentages.}}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passsing \\
    \midrule
    \jsc{} & \Fix{2278}\\
    \veight{} & \Fix{1213} \\
    \chakra{} & \Fix{7041} \\
    \smonkey{} & \Fix{1761} \\
    \bottomrule 
  \end{tabular}
  \normalsize
\end{wraptable}

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ standard. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. It is important to note that failures are
expected as it takes time for engines to adjust to the
spec.\Mar{...mention the variance was negligible...} We noticed that
all four engines we analyzed but \chakra{} use some variant of the
Test262 suite as part of their regression process, but we used the
same version in this experiment, the one available from the Test262
web site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \jsc\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this test suite indicates missing features
as opposed to bugs. However, note that \chakra\ is both the engine
that has the lowest passing ratio in the conformance test suite and
the one we were able to find more confirmed bugs (as per
Figure~\ref{fig:summary}). We conjecture that the development age of
the engine--Chakra is the newest engine\Fix{find DOB of
  Chakra}--justify both observations.

%% The rationale is that lack of support
%% to features (as measured by conformance testing) and reliability of
%% engines (as measured in this study) may have some relationship.

\subsection{Test Transplantation}
\label{sec:transplantation}

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}
